\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-10-30 parts-grn.tex
Minor typo fix

\modMM{In this paragraph, we} concisely present Thomas' modeling of a Biological Regulatory Network (BRN) and its dynamics, merely inspired by
\cite{Richard06,BernotSemBRN}.
In order to enlarge the class of Thomas' models compatible with PH dynamics (w.r.t.~the presented
inference),
we propose the notion of unsigned edge modeling an interaction whose nature (activation or inhibition) is undetermined,
and we extend the classical parametrization formalism by setting parameters to intervals of values instead of single values.
We briefly discuss these additions.

@@

\modMM{The IG is not sufficient to unambiguously define the dynamics of the system. In particular, a component may be regulated by both a positive and negative interaction derived from two different components. To refine the dynamics, a parametrization had been added to the model \cite{snoussi1989qualitative}. This parametrization allows to define focal points, i.e. it clarifies the level towards which a component evolves depending on the expression of its regulators.
Some of the information included in the IG and the parametrization may appear as slighltly redundant. Especially, if the single parametrization were enriched with additional constraints (e.g., monotonicity requiring an ordering on the value of parameters), then it may directly capture the signs. However, distinguishing the IG and parametrization allows to decouple the graph (which is generally one of the prior knowledge from the biologists) from the constraints on its dynamics. It opened the way to numerous studies (e.g., necessary condition on sustained oscillations) solely based on the structure of the IG, e.g., the analysis of positive or negative circuits.}

>>>>

\modMM{In this paragraph, we} concisely present Thomas' modeling of a Biological Regulatory Network (BRN) and its dynamics, merely inspired by
\cite{thomas1990biological, Richard06,BernotSemBRN}.
In order to enlarge the class of Thomas' models compatible with PH dynamics (w.r.t.~the presented
inference),
we propose the notion of unsigned edge modeling an interaction whose nature (activation or inhibition) is undetermined,
and we extend the classical parametrization formalism by setting parameters to intervals of values instead of single values.
We briefly discuss these additions.

@@

\modMM{The IG is not sufficient to unambiguously define the dynamics of the system. In particular, a component may be regulated by both a positive and negative interaction derived from two different components. To refine the dynamics, a parametrization had been added to the model \cite{snoussi1989qualitative}. This parametrization allows to define focal points, i.e. it clarifies the level towards which a component evolves depending on the expression of its regulators.
Some of the information included in the IG and the parametrization may appear as slighltly redundant. Especially, if the single parametrization were enriched with additional constraints (e.g., monotonicity requiring an ordering on the value of parameters), then it may directly capture the signs. However, distinguishing the IG and parametrization allows to decouple the graph (which is generally one of the prior knowledge from the biologists) from the constraints on its dynamics. It opened the way to numerous studies (e.g., necessary condition on sustained oscillations) solely based on the structure of the IG (e.g., the analysis of positive or negative circuits).}
